\section{Evaluation}
\label{sec:middleware_qualitative_evaluation}

With the solution presented in the previous section, we aimed to retain the desirable properties of both \ac{rest} and \ac{tsc}.
% analísis más largo en la siguiente sección
% 1. cómo sé que esto es mejor que usar REST y TSC por separado? Sinergia?
% 2. que aporta unirlo bajo un mismo middleware?
% 3. tiene beneficios?
However, some questions arise from that integration:
(1) does in fact retain all the properties of \ac{rest} and \ac{tsc} separately? Otherwise, which properties are affected?
(2) what other benefits carries comparing with using already existing \ac{tsc} and \ac{rest} middleware?

% Fielding distingue entre:
%      + "distributed-system": hace que el usuario vea el sistema como un todo, sin saber cuando se realizan llamadas en remoto y cuando no
%      + "networking-system": no necesariamente oculta las particularidades de la red <- el se centra en estos


To answer these questions, we analyze the presented solution from different point-of-views:
(1) its coordination properties (Section~\ref{sec:XXX_properties}),
(2) its network-level properties (Section~\ref{sec:network_properties}),
(3) how the latter work together to contribute to the challenges of an \ac{ubicomp} environment (Section~\ref{sec:middleware_properties}).
Section~\ref{sec:middleware_eval_summary} summarizes these analysis. % cómo dan respuesta a las preguntas del comienzo


% TODO cosas rescatables del paper original de WoT 2011:
%     Uniform API vs. specific usage of each API !!!
%     Coupling: lo comido (autonomies), por lo servidor (client-server coupling por tener API común)
%          In spite of the outlined decoupling nature of both approaches, the data definition can be considered a coupling mode indeed.
%          While in \ac{wot} each resource defines its own data formats and contents themselves, in \ac{tsc} the ontology in which the semantic
%          concepts are described must be known by each part of a distributed application to effectively cooperate among them.
%     Discovery: HATEOAS puede ser complejo para cacharros peques (parseo),
%                proponemos discovery basada en API uniforme y a nivel de cacharros con algún mecanismo en el que no entramos.
%          One of the main drawbacks in \ac{wot} is the lack of a discovery mechanism for new objects and the data they provide.
%          Even when this data can be linked in each object response (using HATEOAS) and microformats are sometimes included to ease the search-ability of these objects by search engines, it is difficult for an object which may change of location and context to be referred.
%          Thus, \ac{wot} may have a tendency to create isolated islands of data.
%          Several workarounds have been proposed to overcome this limitation, such as using a central repository\footnote{http://www.pachube.com/}, a framework which uses federated repositories responsible for different administrative domains \citep{stirbu_towards_2008} or making each connected sensor announce itself to let an intermediary know its presence \citep{kamilaris_smart_2010}.

%     Scalability: se ha hablado y ahora no es tan mala como antes ;-) Entre cacharros seguiría dando asco
%     Semantics: Microformats vs Full (hablar de esto)
%     Comprensión por parte de usuario: sencillo misma interfaz, no tienes que andar descubriendo nuevas APIs y viendo cómo funcionan, qué formato devuelven, etc.
%     Comprensión por parte de desarrollador: API sencillica siempre


\subsection{Coordination properties}
\label{sec:coordination_properties}

% TODO añadir la autonomía que se refería a la semántica?
As we have already discussed in Section~\ref{sec:integration}, indirect communication middleware can have two key properties:
\begin{itemize}
  \item The sender does not need to know the receiver or receivers and vice versa (i.e. \emph{space uncoupling}).
  \item Senders and receivers do not need to exists in the same time to communicate with each other (i.e. \emph{time uncoupling}).
\end{itemize}


The primitives used in our space-based computing implementation force it to be \emph{space uncoupled}.
On the contrary, it is not always \emph{time uncoupled}.
If two nodes write and read from the coordination space, they are \emph{time uncoupled};
but if a node accesses to others' content (i.e. \emph{self-managed graphs}), they are not.
In other words, \emph{time uncoupling} is not achieved by the extension of the model presented in Section~\ref{sec:halfway_solution}.
As a future work, this could be alleviated by a caching mechanism implemented in the space holder or holders. % TODO hablar con propiedad de esos elementos => nombrarlos antes
% see \ref{tab:middleware_coordinationprop}

\input{\pathchapthree/tables/coordination_properties}


\subsection{Networking properties} % Architectural Properties for Network-based Styles
\label{sec:network_properties}
% Cómo afecta la app propuesta => ir actualizando al final de otras secciones???

In Section~\ref{sec:tsc_vs_rest} we have described how \ac{tsc} does not contradict any of the \ac{rest} principles.
However, the adaptation presented in this thesis does not completely adhere to the \ac{rest} style.
In this section we present how this divergences affect the \ac{rest}'s properties.
% decir que el objetivo final es que pudiera ser REST

% TODO antes de entrar al lio, explicar cómo funciona esto de REST, en qué parte de nuestra solución lo necesitaremos
% decir que API para TSC mola
% decir que API para los cacharros deberia de ser independiente a lo que nosotros digamos y por eso estaria bien REST
%     de todas formas, como es dificil, nos quedamos en un nivel de madurez menor


In \citeauthor{fielding_architectural_2000}'s words, the relevant properties which describe a network-based system are the following ones \footnote{We refer to the reader to \citet{fielding_architectural_2000} for the complete thorough analysis.}:
% verificar que no se parece demasiado a sus definiciones o sino poner cursiva.
\begin{description}
  \item[Performance] is divided into network performance, user-perceived performance and efficiency.
    \begin{description}
      \item[Network performance] is affected by the styles in the number of interactions and the granularity of data elements.
      \item[User-perceived performance] refers to the impact a user in front of an application perceives. % UP Performance es una feature que no aporta mucho a nuestro caso
      \item[Efficiency] is achieved by minimizing the use of the network.
    \end{description}
  \item[Scalability] measures how an architecture supports a big amount of components and interactions between them.
  \item[Simplicity] is achieved through the separation of concerns for the components and the generality of architectural elements.
  \item[Modifiability] indicates how easily gradual changes can be introduced in the system.
                       These changes form different implementations which should coexist.
                       % Dynamic modifiability avoids the whole system to restart.
    \begin{description}
      \item[Evolvability] refers to the degree in which a component can be implemented without negatively impacting on others.
      \item[Extensibility] measures the ability to add functionality to the system.
      \item[Customization] is the ability to customize the behavior of an architectural element temporarily.
      \item[Configurability] is related with the extensibility and the reusability.
      \item[Reusability] is the ability to reuse components, connectors or data elements without modifying other apps.
    \end{description}
  \item[Visibility] is the ability of a component of monitoring or mediating in the interaction between other two components.
  \item[Portability] is the ability of working in different environments.
  \item[Reliability] is the degree in which an architecture depends on the failures of the system or components, connectors or partially incorrect data.
\end{description}

% Requisitos de ealy web, propiedades deseables
%   Low entry-barrier
%   Extensibilidad
%   Distributed Hypermedia
%   Internet-scale

The Table~\ref{tab:network_properties} summarizes how different architectural styles achieve these properties.
Particularly, it shows the styles from which \ac{rest} derives (see Section~\ref{sec:rest}).
The ultimate goal of the solution explained in the previous section is twofold:
\begin{enumerate}
  \item Provide a \ac{rest} access to a semantic space.
       This would ease its integration with the rest of the web.
  \item Enrich that space with the knowledge provided by other \ac{rest} \acp{api}.
\end{enumerate}
Therefore, ideally, its networking properties would be the sames as the \ac{rest} style.


However, defining a 100\% \ac{rest} compliant \ac{api} is not easy.
Indeed, most of the self-proclaimed \ac{rest}ful \acp{api} are not \citep{house_how_2012}. % la nueva buzz word para eso: hypermedia API
The main cause is the \emph{HATEOAS} constraint seen in the Section~\ref{sec:rest} \citep{fielding_rest_2008}.
Using \ac{http} as an application-level protocol forces a developer to comply the rest of the constraints \citet{moore_hypermedia_2010}, but not \emph{HATEOAS}.
% TODO hablar del Richardson Maturity model!


% semantic-based \ac{api} is not easy. => referencias a los que lo han intentado, a que no hay hipertexto, a que te puede interesar inferir con bastantes
Regarding the \ac{sw}, some recent efforts have tried to move closer to the \ac{hypermedia} constraint \citep{steiner_fulfilling_2011,kjernsmo_necessity_2012}.
However, these worlds remain quite isolated.
In fact, \ac{sw} API  usually present another main divergence with the \ac{rest} style: the use of query endpoints.
% i.e. no devuelven listas de enlaces, sino todo a lo bruto
% esto quiere decir que no se devuelve todo y ala, tu procesa esa burrada de datos, más bien se filtran
These endpoints intend to solve some inefficiency issues which \ac{rest} shows when working with a big amount of data. % TODO mencionar \ac{lod} en algún punto de aquí?
To that end, they allow expressive query languages and offer results where the boundaries of the different resources often blurs \citep{wilde_restful_2009}.
The most paradigmatic case may be to decide to which graph does a inferred content belongs. % ejemplo de lo anterior


% Aterrizar esto a IoT y a nuestro caso:
%        La eficiencia es importante => para evitar hacer 500 llamadas a un cliente
%        La reusabilidad es importante también => para potencialmente adaptarse a cualquier WoT semántico
%           en el futúro => más trabajo en este área
%       Solución de compromiso:
%           nivel de madurez X de Richardson. Suponemos que alguien debe serguir nuestro API mínimo en los objetos WoT

In \ac{iot} both the efficiency on the communications and reusability of the \ac{api} are important:
\begin{description}
  \item[Efficiency:] mobile and embedded devices' have restricted energy autonomy.
                    This autonomy is severely affected by network communications. % TODO cite
                    Particularly, the access to the data they provide by means of hyperlinks may result in many HTTP requests. % aunque eso se puede adaptar por lo visto
                    %  Por que sería muy costoso hacer rollo araña?!
		    %     lo que ganas de reusabilidad, lo aumentas en complejidad en el cliente
                    %     interpretar código del servidor no es tampoco super-sencillo (xHTML!)
  \item[Reusability:] due to the heterogeneity of the devices, assuming that they all share a common and unevolvable \ac{api} may not be realistic. % TODO paliar para que no parezca que no tiene sentido
\end{description}
The first solution together with the current difficulties on achieving a fully and standard \emph{HATEOAS} for machines in the \ac{sw}, lead us to opt for the second level on the Richardson Maturity level.
Besides, our \ac{tsc} \ac{api} will be \emph{HATEOAS} \ac{api} in its humans representation to ease their learning level.% pero aún así el API de TSC seguirá siendo HATEOAS para los usuarios, no para las máquinas
However, we do not discard to work towards a fully \ac{rest}ful \ac{api} as future work.


In conclusion, the properties of the properties for network communication style we adopted corresponds with \emph{LCODC\$SS} plus simplicity and visibility. % hacer una nueva fila con esto
% TODO comprobar que se explica eso tal cual en la tesis de Fielding: HATEOAS => sólo afecta a reusabilidad

% TODO Comprobar que no se salga por el borde derecho!
\input{\pathchapthree/tables/network_properties}



\subsection{Properties for \acs{ubicomp}}
\label{sec:middleware_properties}

A middleware is a software layer which provides a higher level of abstraction and masks the underlying heterogeneity.
The middleware presented in this thesis is oriented for \ac{ubicomp} environments and the devices which populate them (i.e. mobile and embedded devices).
Whereas the devices part of the \ac{iot} are a subset of the ones present in \ac{ubicomp}, we consider that the challenges they have to face are the same ones.
For instance, smartphones are not part of the \ac{iot}, but face similar energy and computational limitations as the embedded devices. % posiblemente no todas las propiedades!

% ¿Qué propiedades deseables para IoT añadiríamos?
Therefore, we will adhere to the challenges presented by the \emph{Internet-of-Things Architecture} European project \citep{walewski_project_2011} to analyze our solution.
\citeauthor{walewski_project_2011} state that the \ac{iot} must overcome the following challenges:
interoperability, scalability, manageability, mobility, security and privacy and reliability.
Furthermore, we also consider energetic and computational constraints which devices in \ac{ubicomp} have to face. % ponerlo de forma que sea menos pegote?


% TODO cómo las distintas propiedades vistas antes se combinan para aportar a estas
Table~\ref{tab:middleware_netprop}, shows how the properties explained in the previous sections contribute to achieve these challenges.


% TODO Comprobar que no se salga por el borde derecho!
\input{\pathchapthree/tables/middleware_netprop_map}


% TODO ver si tiene sentido hablar de estas cosas
% explicar cómo HTTP trataba de evitar complejidades
% Propiedades que jodes de HTTP de cara al usuario: simplicidad...
% explicar como al crear una capa por encima, complicas todo un poco
%       sencillez
%       user-based library vs a lo otro
% drawbacks frente a HTTP: sencillez, etc.
%A middleware is a software layer which provides a higher level of abstraction and masks the underlying heterogeneity.
%\ac{http} is a middleware indeed, but sacrifices masking exceptions on behalf of the simplicity. % TODO checkear con la tesis de Fielding
% hablar de user-based library vs a lo otro


\subsubsection{Interoperability}

% 2 cosas contribuyen a esta propiedad:
%     Uso de HTTP
%     Semántica => ponerlo como una autonomía (encaja bien en la tablita) o no (en realidad se podría usar tanto sobre TSC como sobre HTTP)?

Interoperability is the key to deal with a wide range of heterogeneous technologies.
The use of both the \textbf{network style} and the \textbf{semantic data} contribute to this challenge.


\paragraph{Semantics}

Using semantics we promote the reuse of data describing them in a more rich and abstract way.
The semantic web is composed by a series of standardized technologies which allow to formally describe the models (i.e. the concepts and how they relate to each other).
Two key mechanisms of the Semantic Web in this aspect are the inference of new data and the mapping of equivalent models.
% hablar de cómo contribuye o no a su portabilidad??
% Besides, the Semantic Web is built on top of well-defined and vastly supported tools.

% Drawbacks
% TODO referencia al paper de qué impide conseguir challenges semánticos


\paragraph{Networking}

For the communication between nodes, we rely on the widely supported \ac{http} protocol. % usar la palabra ubiquitous o pervasive???
Communication with devices using other protocols must be done by means of specialized gateways. % out-of-the-scope
Therefore, adhering to a unique protocol does not help dealing with various communication technologies.

% opción muy común hoy en día para definir APIs
However, a number of current applications use \ac{http} to define their network accessible \ac{api}'s. % through so-called REST APIs
% posiblemente indirectly due to its simplicity => pervasiveness and massive adoption
This makes it a \emph{de facto} requirement to interoperate with these applications. % te da acceso a más apps
% TODO ejemplo de ello: mashups
% también en resource constrained devices: el éxito de WoT es sólo una prueba de ello
In fact, this success has also its counterpart on resource constrained platforms.
The clearer sign for that is the upcoming \ac{wot} initiative.


At a finer grained level, there are several properties which help different \ac{http} implementations to interoperate: % (of interoperability)
\begin{description}
  % \item[Simplicity] => a nivel de red no, pero un middleware simple contribuye a una mayor portabilidad % PROPIEDAD INDIRECTA
  \item[Modifiability] is the ease of gradually introducing changes in the system.
                       Particularly dynamic modifiability avoids restarting the entire system when introducing a change.
                       This property allows different implementations to coexist,
                       reducing issues on the communication between two nodes through \ac{http}.
                       
		      % mejor no meterme en fregados de justificar cada subpunto:
		      % is important due to the \emph{evolvability} and the \emph{reusability}.
		      % Evolvability allows two nodes to have components implemented at different degrees without negatively impacting each other.
		      % contribuyen a eso (sacado de Fielding):
		      %   + CS: The separation of concerns also allows the two types of components to evolve independently, provided that the interface doesn’t change.
		      %   + Layered systems reduce coupling across multiple layers by hiding the inner layers from all except the adjacent outer layer, thus improving evolvability and reusability.
		      % extensibility no: lo introduce COD, así que echa calculos de si me importa esa característica de HTTP
		      % visibility => qué tiene que ver lo fácil que es monitorizarlo con esto?
  
  \item[Portability:] \ac{http}'s portability is backed by the plethora of \ac{http} libraries and frameworks available for most of the computing platforms.
                    % Cachis, no he podido usar una palabra tan molona como: pervasiveness
                    % Justificación: permite interoperar entre distintas plataformas?
                    Consequently, a huge number of platforms can interoperate through \ac{http}.
\end{description}


% No sé dónde meter esta ventaja independiente
% TODO Besides, we enable its \emph{evolvability} in different nodes by allowing them to implement at different degrees (see Section~\ref{sec:status_codes}). % TODO esto es un poco jugón, porque no funcionaría bien sin todo!

Besides, in our \ac{api} \ac{http} the following points remain unsolved:
% estos 2 últimos son como redefinir interop
\begin{itemize} % posiblemente incluir lo que se explica aquí en otro punto
  \item \emph{Using third applications' data}:
  \begin{enumerate}
    \item In Section~\ref{sec:network_properties} we detailed how a pure \ac{rest} \ac{api} contributes to a higher decoupling between clients and servers.
	  This could help to make clients able to autonomously adapt to use different \ac{rest} \acp{api} defined in each device or to different versions of these \acp{api}. % i.e. evolvable
	  Of course, this would come at a cost of more complex clients. % cacharros parseando HTML, interpretandolo, etc.
	  
	  Our \ac{api} is not hypermedia-driven.
	  This requires third applications to implement a uniform \ac{api} on top of them to allow our middleware consume their data.
	  However, the \ac{api} is resource-oriented and simple to implement. % TODO definir qué es y qué no es resource oriented!
	  
    \item Another obstacle for achieving a real application-level interoperability in our middleware is the use of distinct isolated spaces.
	  In other words, two applications using two different spaces would not share their content.
	  Although this could be avoided by defining a default space, as explained in Section~\ref{sec:tsc_soa} their use is justified in terms of scalability.
  \end{enumerate}
  
  \item \emph{Making our data reusable by third applications}:
	
	As explained, we encourage sharing data in resource constrained devices through an \ac{http} \ac{api}. % TODO hacer la distinción de que lo permitimos a través de ambos: 
	Therefore, any other application able to use \ac{http} and manage semantics can reuse data from our middleware.
\end{itemize}


\subsubsection{Scalability}

The high scalability of the chosen architectural network style is negatively affected by the combination of several features:
\begin{itemize}
  \item Data distribution (i.e. accessing to \emph{self-managed graphs})
  \item Lack of hypermedia on the Semantic Web which cannot guide data discovery.
        In other words, a triple location cannot always be discovered following its \ac{uri}. % relacionado con todo aquello de 303 y demás?
        This means that we need an out-of-band searching mechanism as the one presented in the Chapter~\ref{cha:searching}.
\end{itemize}

% TODO TODO TODO resulta que si desacoplas la URI de un espacio de quien la proporciona, el searching mechanism también puede ayudar con eso!!!


\subsubsection{Manageability}

Manageability helps to cope with so many devices allowing them to have an autonomous behavior. % specially in environments where they cannot be controlled through centrality
This autonomous behavior encompasses self-management, self-configuration, self-healing, self-optimization and self-protection.
In this thesis we propose self-managed architecture which eases the searching of self-managed graphs.


\subsubsection{Mobility}

The ability to face mobility situations can be improved through the autonomy brought by the coordination paradigm. % TODO hacer constantes con space y time uncoupling!
First, mobility situations may impede two nodes coexist at the same time.
Thus, \emph{time uncoupling} enables their communication.

The primitives care about the data and not the provider of that data.
Thus, if more than a node provide a content, we make consumers independent of which provides it.


\subsubsection{Security and privacy}
% En una versión nueva hablan de Proof

This property can be considered traversal to any solution and therefore it is considered out-of-the-scope of the thesis.
However, we are currently working on a lightweight security solution \citep{naranjo_lightweight_2012}. % TODO definir mejor esto
For our future work, we are considering to integrate it with the presented middleware.


\subsubsection{Reliability}
% definición de reliability modificada yendo a la fuente de iot-a.eu

Reliability in \ac{ubicomp} is crucial to handle connectivity losses in various \emph{ad hoc}-like ways.
% ver cómo se relaciona con REST
Particularly, \ac{http} handles it through caching.
% Honestidad: This feature has not been properly addressed in our middleware.


\subsubsection{Limited Computation}

% depende de lo limitado que sea el cacharro, puede ser tan así como XXX
Mobile and embedded devices impose computation restrictions.
This restrictions result in unacceptable response times from the application perspective.
Due to \ac{http} simplicity, computation complexity is found in semantic processing.
For example, some really limited platforms may found difficult parsing long files.
However, we made the following assumptions:
\begin{itemize}
  \item Data providers will be able to process wildcard-based templates and generate appropriate responses from their self-managed graphs.
  \item Data consumers are able to process the responses they receive at least in one semantic format. % por ejemplo :-P
\end{itemize}


Beyond that point, our middleware will not impose anything.
This means that the middleware owner cannot assume:
\begin{itemize}
  \item The inference process on data providers.
        Reasoning over the content to provide unstated knowledge must be desirable.
        Still, most of the mobile and embedded device are not able to process big amount of data. % TODO citar WoT2012
        Besides, reasoners are not available in all platforms.
  \item The inference process on data consumers.
        Another alternative or complement for inferring data on the providers is to do it in the consumers after receiving the responses.
        Again, it is a desirable property, but our middleware does not require it.
  \item General use of more complex query languages.
        Their expressibility benefits the network performance since they can restrict the results returned.
        However, parsing them is not be trivial and parsing libraries are unavailable for some platforms.
        Therefore, a provider cannot assume that providers know how to process something beyond the wildcard based templates.
        As an alternative, providers can decompose these queries in simpler wildcard based templates and locally process the results afterwards (filtering them).
        % This is out of the scope.
	% TODO \subsection{Querying Distributedly over the Space} => optamos por no meternos en jardines y up to the middleware implementer to decide each ;-)
	% condiciones relajadas: consistencia, razonamiento distribuído
	% out of the scope: cómo implementarlo
	% optaremos por lo más sencillo
\end{itemize}


% por eso, el mecanismo de búsqueda se hace en los cacharros más potentes
The searching mechanism explained in the Chapter~\ref{cha:searching} takes into account computing limitations.



\subsubsection{Limited Energy}

% 2 cosas contribuyen: computación y networking => TODO mostrar diagrama de FoxG20
Both computing data and networking operations directly affect energy consumption.
As an example, Figure~\ref{XXX} shows the energy consumption on an embedded platform in an inactivity state and networking and computing data. % más detalles en la sección correspondiente
There are some crucial characteristics which negatively affect energy autonomy of resource constrained devices:
\begin{itemize}
  \item Too complex computation tasks.
	 % They result in excessive networking throughput in some occasions.
        As explained in the previous section, semantic processing is the clearest example of that.
        % como se ha explicado: hemos limitado
        We have limited its impact on resource constrained platforms through the searching mechanism.
  \item Regarding \ac{http}, its stateleness contributes to a bad \textbf{network performance}.
        Besides, the verboseness of most of the semantic formats also contributes negatively to that aspect.
\end{itemize}


On the other hand, we contribute to energy saving minimizing network usage (i.e. \emph{network efficiency}) at different levels:
% efficiency: minimizar el uso de la red
\begin{itemize}
  \item \ac{http}'s network \emph{efficiency} can be improved with \emph{code on demand} and \emph{caching}.
  % por eso, el mecanismo de búsqueda se hace en los cacharros más potentes
  \item The searching mechanism improves \emph{recall} and \emph{precision} (see Chapter~\ref{cha:searching}).
\end{itemize}



\subsection{Summary}
\label{sec:middleware_eval_summary}

In the previous sections we have get to the bottom of the strengths and weaknesses of our proposal.
%  Ventajas/inconvenientes frente a WoT:
%      comunicación indirecta para cacharros
%          local+ref
%              de contenidos relativos a coordinación
%              podríamos cachear contenidos de otros en el espacio central (reliability+energy)
%          ref
%              sacar a colación los problemas aquellos de query sobre muchos recursos
As regard of other semantic \ac{http}-based solutions, the solution presented provides a better handling of mobility situations. % e.g. wot
The uncoupling properties which provide it come at the cost of simplicity to implement the middleware.
%   Para TSC (respecto a otras como Smart-M3):
%      limitamos qué gestiona la entidad central => sólo coordinación, el resto lo coge de los cacharros
%      se reconoce su autonomía permitiendo gestionarse su propio contenido => REST, escalabilidad
%      interop => SW y posibilidad de extender a otros servicios REST
%      multiplataforma => facilidad para portarlo
The main strengths of our \ac{tsc} middleware is that it enriches the coordination properties with semantic content provided by embedded and mobile devices.
Also, it pursues interoperability with other \ac{http}-based applications.

Within its main weaknesses we found performance problems and a coupling between applications due to a no-hypermedia driven \ac{api}.
The performance problems may result of handling semantic data and are particularly important for resource constrained devices.
The coupling between applications is solved through a mandatory \ac{http} \ac{api}, but it complicates reusing third applications' data.


% Ventajas de meclar 2 cosas aparentemente separadas?
% what benefit will derive from the integration of both approaches?
The benefits of bringing together \ac{tsc} and \ac{http} is an unified and simple \ac{api} for the developer. % lo de simple no está demostrado
Due to the primitives' simplicity and to the standard and well accepted technologies uses (i.e. \ac{http} and \ac{semantic} standards), this \ac{api} can be ported to a range of platforms.