% ----------------------------------------------------------------------

\begin{savequote}[50mm]
I woke up one morning thinking about wolves and realized that wolf packs function as families.
Everyone has a role, and if you act within the parameters of your role, the whole pack succeeds, and when that falls apart, so does the pack.
\qauthor{Jodi Picoult}
\end{savequote}


\chapter{Searching in a Distributed Space}
% ó Energy-aware Architecture for Information Search in the Semantic WoT
\label{cha:searching}
\newcommand{\pathchapfour}{4_search}


\newcommand{\Space}{\emph{Space}} % en mayúsculas porque \space ya existe
\newcommand{\Spaces}{\emph{Spaces}} % en mayúsculas porque \spaces ya existe
\newcommand{\consumer}{\emph{Consumer}}
\newcommand{\consumers}{\emph{Consumers}}
\newcommand{\provider}{\emph{Provider}}
\newcommand{\providers}{\emph{Providers}}
\newcommand{\clue}{\emph{clue}}
\newcommand{\clues}{\emph{clues}}


% the code below specifies where the figures are stored
\ifpdf
    \graphicspath{{\pathchapfour/figures/PNG/}{\pathchapfour/figures/PDF/}{\pathchapfour/figures/}}
\else
    \graphicspath{{\pathchapfour/figures/EPS/}{\pathchapfour/figures/}}
\fi


%------------------------------------------------------------------------- 

% Mini-intro para enmarcar esta sección en el capítulo
In Chapter~\ref{cha:tsc} we presented a \ac{tsc} model for \ac{ubicomp} environments which is composed by two areas: coordination space and the outer space.
The \emph{outer space} is formed by the semantic data provided (\emph{self-managed graphs}) by any participant device.
Searching for a graph in that \emph{outer space} is not trivial because it is composed by dynamic and unrealiable devices.

In this chapter, we present an architecture to enable searching for semantic content in a decentralized energy efficient manner.
This searching mechanism can be generalized to other \ac{wot} solutions and scenarios.
To empathize this, during the rest of the chapter we avoid explicitly mentioning the \ac{tsc} middleware or related concepts (e.g. \emph{outer space}).

% TODO IMAGEN de DÓNDE encaja el searching mechanism?
% TODO ver si se joden las propiedades de TSC expuestas anteriormente! (e.g. stateless o lo que sea)



The remainder of this chapter is organized as follows:
Section~\ref{sec:search_intro} gives an overview of the problem addressed.
Section~\ref{background} discusses the related work.
Section~\ref{proposal} presents in detail our energy-aware architecture.
Section~\ref{sec:clues} describes the information that devices exchange to maintain this architecture.
Section~\ref{environment} presents our experimental environment and Section~\ref{results} evaluates our solution.
Finally, Section~\ref{conclusion} states the conclusions of our work.


%------------------------------------------------------------------------- 

% comprobar y aplicar los ultimos cambios y ajustes introducidos en el svn de IJWGS!
\input{\pathchapfour/1_intro}
\input{\pathchapfour/2_relatedwork}
\input{\pathchapfour/3_proposal}
\input{\pathchapfour/4_environment}
\input{\pathchapfour/5_evaluation}
\input{\pathchapfour/6_conclusions}


% ----------------------------------------------------------------------

