% ----------------------------------------------------------------------

\begin{savequote}[50mm]
If you live among wolves you have to act like a wolf.
\qauthor{Nikita Khrushchev}
\end{savequote}


\chapter{Remote Actuation}
\label{cha:actuate}


\newcommand{\restdesc}{\emph{RESTdesc}}


% the code below specifies where the figures are stored
\ifpdf
    \graphicspath{{\pathchapsix/figures/PNG/}{\pathchapsix/figures/PDF/}{\pathchapsix/figures/JPG/}{\pathchapsix/figures/}}
\else
    \graphicspath{{\pathchapsix/figures/EPS/}{\pathchapsix/figures/}}
\fi


%------------------------------------------------------------------------- 

In the previous chapter, we presented an energy-aware technique to search on the completely distributed semantic space. % technique, mechanism?
%This search mechanism promotes the end-to-end interaction between the objects.
However, acting over an \ac{ubicomp} environment is as important as observing what happens on it.
Although this dissertation describes this problem less thoroughly, we consider interesting to discuss it to provide the complete story. %not leave loose ends. % transmit a broader vision. % the big picture

\bigskip

This chapter presents and compares two techniques to change the physical environment.
The first technique is based on common \ac{ts} usage patterns while the second one relies on semantically described \ac{rest} services to create a plan to fulfil a given goal.

Note that the second actuation technique is out the scope of the space-based communication covered in this dissertation.
However, the seamless integration of these \ac{rest} services opens the door to reuse the capacities of many existing devices.
Therefore, we propose reusing the \acs{http} \acsp{api} of already existing semantically described providers.
% without adapting them to the space-based computation. % a nivel practico hacemos más fácil empezar a usar nuestro middleware

This chapter explores this reuse helped by a simple real-world scenario.
The goal of the scenario is to remotely change the light of a lamp.
% % TODO TODO TODO The implementation is publicly available at THIS URL.


\bigskip

The rest of this chapter is organized as follows.
% IG TODO un problema global que veo es que no tienen nombrecitos intuitivos las tecnicas con su \emph{} y sus cosas. Los tienes mas o menos, pero ponerlos explicitos ayudaria. Ahora son "Space-based actuation" y el otro "Direct consumption of REST services" (creo que este deberia ser "Direct actuation" o asi), a ver si puedes encontrar algo que se vea que es una tecnica y otra (de hecho estaria tambien la tercera que seria algo como "Hybrid actuation").
Sections \ref{sec:actuation_space} and \ref{sec:direct_actuation} present the two techniques and their corresponding implementations of the baseline scenario. % se entiende que es de luces
Section~\ref{sec:actuation_comparison} compares these techniques and Section~\ref{sec:actuation_discussion} explores how they can interoperate. % no funciona en ambos sentidos, igual habría que especificarlo!
%Specifically, it presents a consumer willing to indirectly actuate through a space in a semantically described \acs{http} provider. % no sé si queda muy claro
% TODO IG ya te he comentado antes, pero esto de decir que antes presentas la implementacion que extiende el espacio, no me encaja aqui. Quitaria esta frase de entrada, y describiria mejor lo de discusses further...
After presenting a neat solution which only extends the \Space{} implementation, Section~\ref{sec:actuation_discussion} discusses further implementation alternatives.
Finally, Section~\ref{sec:actuation_summary} concludes the chapter.



% ----------------------------------------------------------------------


\input{\pathchapsix/1_ts_patterns}
\input{\pathchapsix/2_goal_services}
\input{\pathchapsix/3_comparison} % de los dos anteriores
\input{\pathchapsix/4_interoperation}
\input{\pathchapsix/5_discussion}
\input{\pathchapsix/6_summary}