% ----------------------------------------------------------------------

\begin{savequote}[50mm]
The original idea of the web was that it should be a collaborative space where you can communicate through sharing information.
\qauthor{Tim Berners-Lee}
\end{savequote}


\newcommand{\codigo}[1]{``\texttt{#1}''}
\newcommand{\primquery}{\emph{query}}
\newcommand{\primread}{\emph{read}}
\newcommand{\primtake}{\emph{take}}
\newcommand{\primwrite}{\emph{write}}

% Model proposal
\newcommand{\coordspace}{\emph{coordination space}}
\newcommand{\outerspace}{\emph{outer space}}
\newcommand{\coordinator}{\emph{coordinator}}
\newcommand{\coordinators}{\emph{coordinators}}
\newcommand{\asteroids}{\emph{asteroids}}
\newcommand{\asteroid}{\emph{asteroid}}
\newcommand{\selfgraphs}{\emph{self-managed graphs}}
\newcommand{\osapi}{\emph{OSAPI}}


\chapter{Triple Spaces for Constrained Devices}
\label{cha:tsc}

% the code below specifies where the figures are stored
\ifpdf
    \graphicspath{{\pathchapfour/figures/PNG/}{\pathchapfour/figures/PDF/}{\pathchapfour/figures/}}
\else
    \graphicspath{{\pathchapfour/figures/EPS/}{\pathchapfour/figures/}}
\fi



% ----------------------------------------------------------------------



% TODO TODO TODO me he dado cuenta que si quiero interoperar, la clave sería meter en algún lado algo sobre LOD y SPARQL Update 1.1!!!
% Igual que quiero interoperar con Semántic WoT, debería interoperar con LOD !!!



In recent years, the \acf{iot} has become a reality due to the increasing number of everyday objects equipped with computing and networking capabilities.
The use of these objects together with the rising of mobile computing greatly contributes to the \ac{ubicomp} vision.
%In the beginning the community put more effort on those devices' connectivity issues, materialized in the spread of technologies such as Zigbee\footnote{http://www.zigbee.org}, 6LoWPAN\footnote{http://datatracker.ietf.org/wg/6lowpan/charter/} or Bluetooth\footnote{http://www.bluetooth.com}.
%However, nowadays it is focusing on the architectural solutions used by the applications built around these objects.
%A classification of these solutions has been already presented in the previous chapter. % Coulouris et al.
This vision can benefit from \acf{tsc} paradigm's decoupling properties. % mencionarlas? citar a alguien que diga que TSC puede molar para eso?
However, other properties are derived from how \ac{tsc} is materialized. % materialized puede sonar mal, pero implemented suena muy umpa-lumpa


This chapter focuses on this materialization, i.e. the design of our own space model.
To that end, Section~\ref{sec:guiding_principles} discusses the principles which guide our proposal.
Section~\ref{sec:hybrid_solution} proposes a mix model which encompasses
\begin{enumerate*}[label=\itshape(\alph*\upshape)]
  \item an independent space which can be used for coordination purposes, and
  \item an enriched view of this space which also shows the information provided by autonomous devices.
\end{enumerate*}
Section~\ref{sec:align_tsc_http} describes a \ac{rest}-like \ac{api} to access the first space.
Section~\ref{sec:federated_space} details the additional extensions needed to support the enriched view.
Finally, Section~\ref{sec:middleware_qualitative_evaluation} evaluates the properties achieved with this model.


\input{\pathchapfour/1_guiding_principles}
\input{\pathchapfour/2_hybrid_solution} % o halfway solution?
\input{\pathchapfour/3_http_alignment}
\input{\pathchapfour/4_federated_spaces}
\input{\pathchapfour/5_evaluation}
\input{\pathchapfour/6_summary}