\section{Thesis outline}
\label{sec:Outline}

% TODO hacer un esquemita chulo con las distintas partes en colores e irlo poniendolo parcialmente en cada sección

The remainder of this dissertation is structured as follows:
Chapter~\ref{cha:background} contextualizes the thesis.
Chapter~\ref{cha:stateoftheart} first presents and compares some relevant works from the field of \acl{ubicomp}. % se entiende que en ambos casos es sobre ubicomp?
It then analyses the state of the art on existing semantic space-based solutions and scrutinizes their advantages and limitations.

Chapter~\ref{cha:tsc} proposes and analyses a model to adapt \ac{tsc} to the \ac{ubicomp}.
This model involves limited devices by enabling them to autonomously manage their own knowledge and later enrich the space with it.
Simultaneously, it preserves most of the space-based computing benefits through a classical space model.

Chapter~\ref{cha:searching} describes the core of this thesis.
It presents an energy-aware search architecture.
This architecture dynamically adapts to the needs of resource-constrained devices.
The goal of this architecture is two-fold:
\begin{enumerate*}[label=\itshape\alph*\upshape)]
  \item to promote direct and fully distributed communication between devices;
and, at the same time,
  \item to reduce network communications between them, particularly the ones directed to the less powerful devices.
\end{enumerate*}

Chapter~\ref{cha:actuate} explores two different mechanisms to change the physical environment using \ac{tsc}.
Ideally, these changes should be produced by writing new semantic information into the space. % a tasks-based approach
However, there is a range of actuators which already use \ac{rest} services whose actuation capacities could be reused.
To achieve this, we propose an alignment between both approaches. % a seamless alignment?


Each chapter evaluates our proposals, discusses the related work, and states our intermediate conclusions. % TODO comprobar que eso sea así al final

Finally, Chapter~\ref{cha:conclusions} states the conclusions of this thesis.
It remarks its advantages and limitations and discusses the achieved goals.
We also explain the lessons learnt and future areas of research on this topic. % TODO comprobar que hay algo que se pueda interpretar como "lessons"