% ----------------------------------------------------------------------

\begin{savequote}[50mm]
I woke up one morning thinking about wolves and realized that wolf packs function as families.
Everyone has a role, and if you act within the parameters of your role, the whole pack succeeds, and when that falls apart, so does the pack.
\qauthor{Jodi Picoult}
\end{savequote}


\chapter{Searching in a Distributed Space}
% ó Energy-aware Architecture for Information Search in the Semantic WoT
\label{cha:searching}


\newcommand{\Space}{\emph{Space}} % en mayúsculas porque \space ya existe
\newcommand{\Spaces}{\emph{Spaces}} % en mayúsculas porque \spaces ya existe
\newcommand{\consumer}{\emph{Consumer}}
\newcommand{\consumers}{\emph{Consumers}}
\newcommand{\provider}{\emph{Provider}}
\newcommand{\providers}{\emph{Providers}}
\newcommand{\clue}{\emph{clue}}
\newcommand{\clues}{\emph{clues}}


% the code below specifies where the figures are stored
\ifpdf
    \graphicspath{{\pathchapfive/figures/PNG/}{\pathchapfive/figures/PDF/}{\pathchapfive/figures/}}
\else
    \graphicspath{{\pathchapfive/figures/EPS/}{\pathchapfive/figures/}}
\fi


%------------------------------------------------------------------------- 

% Mini-intro para enmarcar esta sección en el capítulo
In Chapter~\ref{cha:tsc} we presented a \ac{tsc} model for \ac{ubicomp} environments which is composed of two spaces: the \coordspace{} and the \outerspace{}.
The \outerspace{} is formed by the semantic data provided (\selfgraphs{}) by any participating device.
Searching for a graph in that \outerspace{} is not trivial because it is composed by dynamic and unreliable devices.

This chapter presents an architecture to enable searching for semantic content in a decentralized energy efficient manner.
This searching mechanism can be generalized to other \ac{wot} solutions and scenarios.
To empathize this, during the rest of the chapter we avoid explicitly mentioning the \ac{tsc} middleware or related concepts (e.g. \outerspace{}).

% TODO ver si se joden las propiedades de TSC expuestas anteriormente! (e.g. stateless o lo que sea)


This chapter is organized as follows:
Section~\ref{sec:search_intro} gives an overview of the problem addressed.
Section~\ref{background} discusses the related work.
Section~\ref{proposal} presents in detail our energy-aware architecture.
Section~\ref{sec:clues} describes the information that devices exchange to maintain this architecture.
Section~\ref{environment} presents our experimental environment and Section~\ref{results} evaluates our solution.
Finally, Section~\ref{sec:search_summary} states the conclusions of this chapter.


%------------------------------------------------------------------------- 

% comprobar y aplicar los ultimos cambios y ajustes introducidos en el svn de IJWGS!
\input{\pathchapfive/1_intro}
\input{\pathchapfive/2_relatedwork}
\input{\pathchapfive/3_proposal}
\input{\pathchapfive/4_environment}
\input{\pathchapfive/5_evaluation}
\input{\pathchapfive/6_summary}


% ----------------------------------------------------------------------

