\subsubsection{Remote invocation}
\label{sec:remote_invocation}

% TODO definir en algun lado que es REST y que es WS-*???

% De Guinard 2011 rest-vs-ws
% 
% WS-* These services declare their functionality and interfaces in a Web Ser-
% vices Description Language (WSDL) file. Client requests and service response
% objects are encapsulated using the Simple Object Access Protocol (SOAP) and
% transmitted over the network, usually using the HTTP protocol. Further WS-
% * standards define concepts such as addressing, security, discovery or service
% composition. Although WS-* was initially created to achieve interoperability of
% enterprise applications, work has been done to adapt it to the needs of resource-
% constrained devices [10, 13]. Furthermore, lighter forms of WS-* services, such
% as the Devices Profile for Web Services (DPWS)1, were proposed [6].
% 
% REST At the core of a RESTful architecture [3] lie resources that are uniquely
% identified through Uniform Resource Identifiers (URIs). The Web is an imple-
% mentation of RESTful principles – it uses URLs to identify resources and HTTP
% as their service interface. Resources can have several representation formats (e.g.,
% HTML, JSON2 ) negotiated at run time using HTTP content negotiation. In a
% typical REST request, the client discovers the URL of a service it wants to call by
% browsing or crawling its HTML representation. The client then sends an HTTP
% call to this URL with a given verb (GET, POST, PUT, etc.), a number of options
% (e.g., accepted format), and a payload in the negotiated format (e.g., XML or
% JSON). Several recent research projects implement RESTful Web services for
% smart things [2] within what has become to be known as the Web of Things [5].


% De Pautasso 2008
% 
% REpresentational State Transfer (REST) was originally introduc-
% ed as an architectural style for building large-scale distributed hy-
% permedia systems. This architectural style is a rather abstract entity,
% whose principles have been used to explain the excellent scalability
% of the HTTP 1.0 protocol and have also constrained the design of
% its following version, HTTP 1.1. Thus, the term REST very often
% is used in conjunction with HTTP.


As stated before, the \acs{rest}ful style and the set of WS-* standards are probably the most common remote invocation substyles currently used in the Internet.
This section only aims to introduce them, for an extensive analysis on their advantages and disadvantages please refer to \citet{pautasso_restful_2008}.

On the one hand, \ac{rest} architectures are those which follow the design principles described in Section~\ref{sec:rest}.
Each of these principles contribute to different networking properties (see Section~\ref{sec:network_properties}).
The \emph{scalability} and the \emph{simplicity} stand out from these properties in \ac{rest}.
% cita de fielding sobre simplicidad y sobre good at long term-design
% already have many libraries and tools available, which eases the adoption of this style by developers.
The web implements \ac{rest}'s principles.
Therefore, a \ac{rest} solution can rely on well-accepted standards used in the web (e.g. \ac{http}, \ac{uri} or \ac{mime}).
This acceptance also results in a massive availability of libraries in most of the computing platforms.


On the other hand, WS-* standards syntactically describe the services' functionality and interfaces using \ac{wsdl}.
The communication between providers and consumers is usually transmitted over the \ac{http} in messages encapsulated using \ac{soap}.
WS-* web services, also called ``Big Web services'', offer more features such as transactions, reliability or message-level security.
However, they also require further architectural decisions on different layers of the WS-* stack.
These decisions make the people perceive it as more complex than the RESTful style \citep{guinard_search_2011}.
% pensar bien cómo introducir el tema de la simplicidad: por diseño de REST, por las decisiones que hay que tomar en WS-*???
Probably thanks to that perception, \ac{rest} has gained momentum during the last decade. %  simpler alternative for services


Besides the simplicity, another key difference between both approaches is how they use web standards. % (e.g. \ac{http}, \ac{uri} or \ac{mime})
The correct use of the web standards can benefit a \ac{rest}ful design.
On the contrary, WS-* uses some of these standards in ways they were not designed for.
For instance, it uses \ac{http} as a transport layer instead of as an application layer protocol.
This prevents from achieving some of \ac{http}'s desirable properties (e.g. scalability or visibility).


\ac{rest} has gained momentum during the last decade as a way to expose functionality and data because:
% ptos a destacar:
%   simplicidad - menos cosas a implementar = mayor disponibilidad en plataformas
%                 no vuelves locos a los usuarios: menos cosas a decidir
%   mayor funcionalidad a costa de dañar propiedades de los protocolos: e.g. usando HTTP como transporte


% This standards already have many libraries and tools available, which eases the adoption of this style by developers.

\bigskip

The use of both styles in resource-constrained devices is represented by
\ac{dpws} \citep{moritz_devices_2010}, based on WS-*, and the \ac{wot} \citep{guinard_internet_2011}.
However, due to its importance for this dissertation, we only delve into the latter in Section~\ref{sec:soa_ubicomp}. % o mejor poner su tesis?

% TODO reescribir esto para que no suene tan positivo y sobrado
\ac{dpws} defines a subset of WS-* to make it suitable for resource-constrained devices.
%\ac{dpws} is claimed to be used in industrial environments.
Its most remarkable features are: decentralized multicast-based discovery, secure message transmission, subscription and event notifications.
\citet{moritz_devices_2010} compared \ac{dpws} with the \ac{rest} approach coming to the conclusion that \ac{dpws} can be restricted to be fully compatible with the RESTful style.
Even in that case, \ac{dpws} will still cover some missing features of the RESTful approach such as eventing and discovery \citep{moritz_devices_2010}.
% no menciono que sean más pesados para cacharros porque no he encontrado un sitio en el que defiendan que \ac{dpws} lo es (si que hay alguno que comparan REST y SOA, pero no DPWS)



