% ----------------------------------------------------------------------

\begin{savequote}[50mm]
The beginning of wisdom is to desire it.
\qauthor{Solomon Ibn Gabirol}
\end{savequote}


\chapter{Background}
\label{cha:background}

% the code below specifies where the figures are stored
\ifpdf
    \graphicspath{{\pathchaptwo/figures/PNG/}{\pathchaptwo/figures/PDF/}{\pathchaptwo/figures/}}
\else
    \graphicspath{{\pathchaptwo/figures/EPS/}{\pathchaptwo/figures/}}
\fi


%------------------------------------------------------------------------- 

% Megafrase de las que no gustan al primo, pero a mí me gusta su pomposidad ;-)
To clarify the foundations in which our work relies and to provide a starting point for understanding the rest of the thesis,
this chapter introduces, categorizes, and describes the related research topics. % o llamarle research areas, important concepts?
These topics are classified attending to their relation with a critical aspect for \ac{ubicomp}: interoperability.
% TODO valorar meter en otra sección descripción de IoT y UbiComp y sus características?

% Otra forma de ver la interop:
%  La European Telecommunication Standards Institute (ETSI) define cuatro capas:
%      technical interop: a nivel de comunicación (p.e. de acuerdo en las 7 capas de OSI)
%      syntactic interop
%      semantic interop
%      organizational interop


% no habría que definir de nuevo y de manera formal ubicomp o vale con la intro?
The IEEE defines \emph{interoperability} as ``\emph{the ability of two or more systems or components to exchange information and to use the information that has been exchanged}'' \citep{_ieee_1990}.
The heterogeneity of technologies present in \ac{ubicomp} environments makes this a key property to consider.
The definition clearly distinguishes between two requirements: % o goals o incremental requirements
\begin{enumerate*}[label=\itshape\bfseries(\arabic*\upshape)]
  \item \textbf{to exchange} information; and
  \item \textbf{to use} that information. % to understand others data (i.e. \emph{interoperation}).
\end{enumerate*}

\medskip

% Buscar una referencia mejor: http://en.wikipedia.org/wiki/Interoperability
Exchanging information in distributed systems comprehends the communication between two systems.
% lo de ab-initio practicamente sólo lo he visto en la wikipedia
For the lower communication levels, we rely on standard and widely accepted communication protocols (i.e. interoperability \emph{ab-initio}). % e.g. HTTP
For higher-levels (i.e. application layer), this dissertation delves into the \emph{space-based computing} and \ac{rest} architectures.
Section~\ref{sec:soa_integration} categorizes both of them together with other integration approaches.
Then, both integration styles are individually presented in sections \ref{sec:rest} and \ref{sec:tuplespaces_eoa}.

\medskip

% Sintáctica vs semántica
Regarding the second goal, it can be analysed from two perspectives: syntactically and semantically.
On the one hand, \emph{syntactic interoperability} is associated with the format of the data (i.e. its syntax and encoding) \citep{van_der_veer_achieving_2006}. % e.g. high level: HTML, XML, etc.
On the other hand, \emph{semantic interoperability} is concerned with ensuring that the exchanged information has a precise meaning.
Its ultimate goal is to make the information ``\emph{understandable by any other application that was not initially developed for this purpose}'' \citep{_european_2004}.
Section~\ref{sec:soa_sw} describes a prominent movement which is focused on this goal: the \acl{sw}. % TODO qué es la SW??? un mecanismo, conjunto de estándares, ¿?


\input{\pathchaptwo/1_integration}
\input{\pathchaptwo/2_rest}
\input{\pathchaptwo/3_tuplespaces}
\input{\pathchaptwo/4_semantic_web}


% ----------------------------------------------------------------------

